\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
reduce not filled boxes (NumPy and ctypes are in PyGRASS box)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64944 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{
Some API examples to convert a raster map to a numpy array and then back to a raster.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Python script versus GRASS GIS module}}{
and running code from IDE
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS Addons}}{
The GRASS GIS Addons ensure long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS core.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{ctypes interface to C libraries}}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Using NumPy}}{

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Alternatives to Python}}{
GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
and as subprocesses virtually any language as long as proper environment is set.

The GRASS GIS library povides a C API which is commonly used to create GRASS modules in C and C++.

GRASS GIS modules can be used within R using the \pkg{rgrass7} package.
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{PyGRASS interface to C libraries}}{
Some API examples to convert a raster map to a NumPy array and then back to a raster.

@@

In addition to PyGRASS interface, advanced programmers can use \pkg{ctypes} interface
to access C functions from GRASS GIS libraries directly.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{GRASS GIS modules, addons and Python scripts}}{
The GRASS GIS Addons ensure long-term preservation of the code.
Well maintained modules in Addons can be moved to GRASS GIS core.
and running code from IDE
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Alternatives to Python}}{
GRASS GIS API is not limited only to Python.
GRASS GIS modules are command line tools, so they can be used in shell scripting (e.g. Bash)
and as subprocesses in virtually any language as long as the proper environment is set.
The GRASS GIS library provides a C API which is commonly used to create GRASS GIS modules in C and C++ programming languages.
Finally, GRASS GIS modules can be used within R statistical environment using the \pkg{rgrass7} package.
}
